Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2015-01-15 papers/wdmerger_I/paper.tex
a little appendix work

Summary of changes:
\begin{itemize}
\item New reference state/flattening fix: helps energy conservation a
  lot, also fixes some undershoot/overshoots

\item New gravity update type: fixes some energy conservation

\item temperature-based PPM: fixes temperature floors

>>>>

The basic PPM algorithm in CASTRO has undergone a number of changes since
the original code paper \citep{castro}.  A discussion of the pure
hydrodynamics changes was given in \citet{zingalekatz:2015}.  Here
we discuss the changes that affect multispecies flow and source
terms.

Summary of changes:
\begin{itemize}
\item New gravity update type: fixes some energy conservation
